\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{parskip}

\title{Type Synthesis Process}
\date{\today}

\begin{document}
\maketitle

\section*{Type Synthesis Key Design Questions}

\begin{enumerate}[leftmargin=*, label=\textbf{\arabic*.}]
  \item \textbf{How many links and joints are required for the desired degrees of freedom? (See Eqn 1)}\\[0.25em]
  Desired degrees of freedom: 1
  DOF = 3(n-1) - 2f_1 - f_2
  n = 6, f_1 = 7, f_2 = 0
  DOF = 3(6-1) - 2(7) - 0 = 1
  Therefore, 6 links and 7 joints are required.
  \\\vspace{0.75em}

  \item \textbf{What are the link types, and how many of each are needed for this link set? (See Eqn 2)}\\[0.25em]
  n-(DOF+3) = T+2Q+3P
  n = 6, DOF = 1
  T+2Q+3P = 6-(1+3) = 2
  T = 2, Q = 0, P = 0
  2 ternary links, 4 binary links.
  \\\vspace{0.75em}

  \item \textbf{How many different link sets satisfy the desired degrees of freedom?}\\[0.25em]
  Stevenson I, II, and III. Watt I and II.
  \\\vspace{0.75em}

  \item \textbf{How many linkage topologies can be formed from these sets of links?}\\[0.25em]
  \\\vspace{0.75em}

  \item \textbf{How many unique topologies are available from which to choose?}\\[0.25em]
  \\\vspace{0.75em}

  \item \textbf{How many ways can a ground link be chosen for each topology?}\\[0.25em]
  \\\vspace{0.75em}

  \item \textbf{How can one predict if any topologic inversions are inherently better than all others for the task at hand?}\\[0.25em]
  \\\vspace{0.75em}

  \item \textbf{How many ways can the types of joints required to satisfy the task be distributed throughout the linkage?}\\[0.25em]
  \\\vspace{0.75em}

  \item \textbf{How many different links could serve as the input drivers?}\\[0.25em]
  \\\vspace{0.75em}
\end{enumerate}

\end{document}


